### 2019-05-27 thesis.tex
Did some writing
Astrophysical plasmas and definition of plasma (again).

\section{Astrophysical plasmas}
\label{sec:astro-plasmas}
The plasma physics branch of Physics is broad. From life-changing
industrial applications like the plasma processing of integrated
circuits - an essential step of the manufacturing process of tiny
integrated circuits -, passing through the development of the
telecommunications via radio-frequency, to day-to-day devices
like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
important application of plasmas on Earth

>>>>

\section{Astrophysical plasmas}
\label{sec:astro-plasmas}
The first fact that a plasma physics student learns, before even
understanding the definition of plasma, is that most of the baryonic
matter in the universe is in the plasma state. This \emph{most} is
usually estimated to be around $99\%$ \cite{bitt,gurnett2017}. If this
high estimate has something to do with the fact that our probes and
telescopes can only directly detect ionized matter, because it emits
radiation, \cite{chen} it is still a case to be studied.

In order to understand what is a plasma, one must have to be aware of
the differences between the dynamics of neutral and fully ionized gases.
In a neutral gas, assuming that the influence of gravity can be neglected,
the dynamics is dictated by collisions between two components that are
very close to each other. A fully ionized gas, on the other hand, is only
composed of charged particles, that are sources of electric fields. Besides
that, the motion of charged particles generates electric currents, that
will induce magnetic fields. This means that one charge can interact with
several other charges at a considerable distance, through these fields.
Therefore, a partially ionized gas is considered a plasma when its dynamics
is dominated by the electric and magnetic forces of the charged particles,
consequently, a fully ionized gas is also a plasma.

Astrophysical plasmas are observed in a myriad of configurations,
regarding composition, density, temperature, and degree of ionization.
